The \project{unRAVE} catalog

### 2016-09-04 article/unrave.tex
filler text

@@

\subsubsection{Comparisons with Reddy, Bensby, and Valenti \& Fischer}

@@

\subsubsection{Comparison with the \ges\ survey}

\stub{Discuss comparisons with: GES; calibration sources used in \citet{Kordopatis_2013}; and `gold-standard' studies: Reddy, Bensby, Valenti \& Fischer}

>>>>

\subsection{Spectrophotometric distances}
\label{sec:distances}

\stub{These will be derived by Jason Sanders when he returns from his honeymoon.
The timing means that the distances will not be available when we submit the first
version to arXiv. So we may need to remove this section and the reference to it
from the abstract.}

@@

\subsubsection{Comparison with the \citet{Kordopatis_2013} calibration sample}
\label{sec:validation-kordopatis}

\subsubsection{Comparisons with Reddy, Bensby, and Valenti \& Fischer}
\label{sec:validation-gold-standards}

@@

\subsubsection{Comparison with the \ges\ survey}
\label{sec:validation-ges}

There are 142 stars that overlap between \rave\ and the fourth internal
data release of the \ges\ survey. These are a mix of main-sequence, 
sub-giant and red giant branch stars.  Despite most of these stars having
relatively low S/N ratios in \rave\ ($\approx 25$), there is good 
agreement in stellar parameters (Figure~\ref{fig:ges-comparison}.  
The RMS in effective temperature, surface gravity and metallicity is
236~K, 0.39~dex, and 0.18~dex, respectively. 
% TODO: Check if those numbers above are still valid when final catalog is used.

\stub{A paragraph about the abundance agreement.}
